Paper without a name

### 2014-05-30 Article.tex
Changes..
Equation alignment
Add figures

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1.0in]{geometry}
\usepackage[british]{babel}
\usepackage{indentfirst}
\usepackage{array,booktabs,longtable}
\usepackage{multirow}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{url}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{mathtools}
\usepackage{algpseudocode}
\usepackage{algorithm}

@@

@@

This algorithm progressively builds $S$, the table of the elements of $T$ in
increasing order. This is done by progressively inserting the elements of $T$ in
$S$ at a position calculated by the $FindPos$ function. The $FindPos$ function
is based on a binary search, therefore does $O(log(S.size))$ comparisons.

@@

$$u_1 = 0$$
$$\forall n \in \mathbb{N}^*, u_{n+1} = u_n + \ceil{log_2(n)}$$

@@

\begin{figure}
    \centering
    \def\svgwidth{0.7\textwidth}
    \includesvg{svg/boxsys-8-20}
    \caption{Simple non-optimal solution for 8 wires}
\end{figure}

@@

\begin{def*}
$B(q,i) = (q,q+2^i)(q+1,q+1+2^i)\cdots(q+2^i-1,q+2*2^i-1) = \overset{2^{i}-1}{\underset{j=0}{\bigcirc}} (q+j,q+j+2^i)$
\end{def*}
For example: 
$$B(q,0) = (q,q+1)$$
$$B(q,1) = (q, q+2)(q+1, q+3)$$
$$B(q,2) = (q,q+4)(q+1,q+5)(q+2,q+6)(q+3,q+7)$$

@@

@@

$$
\begin{aligned}
    C_8^0 & = & L(3,0) L(3,1) L(3,2) L(3,1) L(3,0) \\
        & = & (0,1)(2,3)(4,5)(6,7) \\
        & & (0,2)(1,3)(4,6)(5,7) \\
        & & (0,4)(1,5)(2,6)(3,7) \\
        & & (0,2)(1,3)(4,6)(5,7) \\
        & & (0,1)(2,3)(4,5)(6,7)
\end{aligned}$$

@@

\begin{figure}
    \centering
    \begin{minipage}{.5\textwidth}
        \centering
        \def\svgwidth{0.7\textwidth}
        \includesvg{svg/boxsys-5-9}
        \caption{Solution for 5 wires}
    \end{minipage}%
    \begin{minipage}{.5\textwidth}
        \centering
        \def\svgwidth{0.85\textwidth}
        \includesvg{svg/boxsys-6-12}
        \caption{Solution for 6 wires}
    \end{minipage}
\end{figure}

@@

$$Perm_0 = { id }$$
$$Perm_{k+1} = Perm_k \cup \left\{ \sigma \circ b_{k+1}, \; \sigma \in Perm_k
\right\}$$

>>>>

\usepackage{color}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1.0in]{geometry}
\usepackage[british]{babel}
\usepackage{indentfirst}
\usepackage{array,booktabs,longtable}
\usepackage{multirow}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{url}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{mathtools}
\usepackage{algpseudocode}
\usepackage{algorithm}

@@

\begin{figure}
 \centering
 \begin{minipage}{.5\textwidth}
    \centering
     \def\svgwidth{0.5\textwidth}
     \includesvg{svg/box0}
     \caption{A switch box with control bit not set}
 \end{minipage}%
 \begin{minipage}{.5\textwidth}
    \centering
     \def\svgwidth{0.5\textwidth}
     \includesvg{svg/box1}
     \caption{A switch box with control bit set}
 \end{minipage}
\end{figure}

@@

This algorithm progressively builds $S$, the table of the elements of $T$ in
increasing order. This is done by progressively inserting the elements of $T$ in
$S$ at a position calculated by the $FindPos$ function. The $FindPos$ function
is based on a binary search, therefore does $O(log(\mathrm{size}(S)))$ comparisons.

@@

$$\begin{array}{r l l}
	u_1 &=& 0 \\
    \forall n \in \mathbb{N}^*, u_{n+1} &=& u_n + \ceil{log_2(n)}
\end{array}$$

@@

@@

\begin{def*}
$$\begin{array}{l l l}
	B(q,i) & = & (q,q+2^i)(q+1,q+1+2^i)\cdots(q+2^i-1,q+2*2^i-1) \\ & & \\
		   & = & \overset{2^{i}-1}{\underset{j=0}{\bigcirc}} (q+j,q+j+2^i)
	\end{array}$$
\end{def*}

For example: 
$$\begin{array}{l l l}
	B(q,0) &=& (q,q+1) \\
	B(q,1) &=& (q, q+2)(q+1, q+3) \\
	B(q,2) &=& (q,q+4)(q+1,q+5)(q+2,q+6)(q+3,q+7)
\end{array}$$

@@

A line is just the union of disjoint blocks of same size, so that all the wires are used by the blocks.

@@

$$
\begin{array}{l l l}
    C_8^0 & = & L(3,0) L(3,1) L(3,2) L(3,1) L(3,0) \\
        & = & (0,1)(2,3)(4,5)(6,7) \\
        & & (0,2)(1,3)(4,6)(5,7) \\
        & & (0,4)(1,5)(2,6)(3,7) \\
        & & (0,2)(1,3)(4,6)(5,7) \\
        & & (0,1)(2,3)(4,5)(6,7)
\end{array}$$

\begin{figure}
    \centering
    \def\svgwidth{0.7\textwidth}
    \includesvg{svg/boxsys-8-20}
    \caption{Representation of $C_8^0$}
\end{figure}

\begin{figure}
    \centering
    \def\svgwidth{0.9\textwidth}
    \includesvg{svg/intuition}
    \caption{Explanation of our intuition leading to the construction of $C_{2^j}^0$}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{minipage}{.5\textwidth}
        \centering
        \def\svgwidth{0.7\textwidth}
        \includesvg{svg/boxsys-5-9}
        \caption{Solution for 5 wires: $C_5^0$}
    \end{minipage}%
    \begin{minipage}{.5\textwidth}
        \centering
        \def\svgwidth{0.85\textwidth}
        \includesvg{svg/boxsys-6-12}
        \caption{Solution for 6 wires: $C_6^0$}
    \end{minipage}
\end{figure}

@@

$$\begin{array}{l l l}
	Perm_0 &=& { id } \\
	Perm_{k+1} &=& Perm_k \cup \left\{ \sigma \circ b_{k+1}, \; \sigma \in Perm_k
\right\} 
\end{array}$$
